Long Term Monitoring of the Disintegrating Planet Candidate KIC 12557548 b

### 2017-05-11 ms.tex
I now show average SC Kepler light curves on top of the individual transits.
Added more background and references to the intro.

\section{Introduction}
The disintegrating planet candidate KIC 12557548 b \citep{rappaport} was the first discovery of a planet candidate causes wildly varying dust obscuration of its host star.
It is now one of many systems that are proposed to be disintegrating planets that are rapidly losing dust that is seen as obscurations toward the host star.

@@

\begin{figure*}
\begin{centering}
\includegraphics[width=0.9\textwidth]{images/all_kic1255_phot/all_kic1255_refcor.pdf}
\caption{Reference-corrected time series photometry \shStar\ for all nights.
The expected transit epochs from the Kepler-based ephemeris \citep{vanWerkhoven2014} are shown as vertical red bars.
Transits are clearly visible for all five nights except for UT2016-06-14.}\label{fig:allNightrefCorrect}
\end{centering}
\end{figure*}

>>>>

\section{Introduction}
The disintegrating planet candidate KIC 12557548 b (hereafter \sha) \citep{rappaport} was the first discovery of a planet candidate causes stochastically varying dust obscuration of its host star.
It is now one of many systems that have stochastically varying transit depths.
The discovery of K2-22b \citep{sanchis-ojedak2-22}, WD 1145+017 \citep{vanderburg2015wdDisintegrating}, KOI 2700 \citep{rappaport2014KOI2700} showed that other systems have similar light curves and can have wavelength-dependent transmission predicted for dust particles \citep{bochinski2015evolving,sanchis-ojedak2-22}.
Furthermore, there are perplexing systems that also display stochastic transit behavior but for which there are still multiple explanations: KIC 8462852 (ie. Boyajian's star) \citep{boyajian846}, RIK-210 \citep{david2017rik210} and PTFO 8-8695 \citep{vanEyken2012ptfTTauri}.

Observational evidence from the \shStar\ system puts constraints on the planet candidate on the system.
Radial velocity velocity variations of the host star put an upper limit on the reflex motion due to the planet and constrains the mass to be $\lesssim 1.2 M_{\mathrm Jup}$ \citep{croll2014}.
There is no detection of secondary eclipses of \sha\ $5 \times 10^{-5}$ in the Kepler bandpass, which means that for an albedo of 0.5, the radius of the planet must be smaller than 4600 km.
The timescale of the variability of the transits gives a mass lot rate of order $\sim M_\oplus/Gyr$, which would indicate a present-day mass of 0.014 $M_\oplus$ when using a radiative-hydrodynamic wind model \citep{perez-becker}.
are proposed to be disintegrating planets that are rapidly losing dust that is seen as obscurations toward the host star.

@@

\begin{figure*}
\begin{centering}
\includegraphics[width=0.9\textwidth]{images/all_kic1255_phot/all_kic1255_refcor.pdf}
\caption{Reference-corrected time series photometry \shStar\ for all nights.
The expected transit epochs from the Kepler-based ephemeris \citep{vanWerkhoven2014} are shown as vertical red bars.
We also show the average Short Cadence Kepler light curves for each of the transit events for comparison with the average.
Transits are clearly visible for all five nights except for UT2016-06-14.}\label{fig:allNightrefCorrect}
\end{centering}
\end{figure*}
